### 2024-05-24 getting-started.qmd
20240524 - add data

@@

@@

>>>>

### The Combine {#sec-combine}

nfl_combine <- progressr::with_progress(
  nflreadr::load_combine(seasons = TRUE))
```

save(
  nfl_combine,
  file = here("data", "nfl_combine.RData")
)
```

load(file = here("data", "nfl_combine.RData"))
```

@@

### Weekly Depth Charts {#sec-depthCharts}

nfl_depthCharts <- progressr::with_progress(
  nflreadr::load_depth_charts(seasons = TRUE))
```

save(
  nfl_depthCharts,
  file = here("data", "nfl_depthCharts.RData")
)
```

load(file = here("data", "nfl_depthCharts.RData"))
```

@@

### NFL Next Gen Stats {#sec-nextGenStats}

nfl_nextGenStats_pass_weekly <- progressr::with_progress(
  nflreadr::load_nextgen_stats(
    seasons = TRUE,
    stat_type = c("passing")))

nfl_nextGenStats_rush_weekly <- progressr::with_progress(
  nflreadr::load_nextgen_stats(
    seasons = TRUE,
    stat_type = c("rushing")))

nfl_nextGenStats_rec_weekly <- progressr::with_progress(
  nflreadr::load_nextgen_stats(
    seasons = TRUE,
    stat_type = c("receiving")))

nfl_nextGenStats_weekly <- bind_rows(
  nfl_nextGenStats_pass_weekly,
  nfl_nextGenStats_rush_weekly,
  nfl_nextGenStats_rec_weekly
)
```

save(
  nfl_nextGenStats_weekly,
  file = here("data", "nfl_nextGenStats_weekly.RData")
)
```

load(file = here("data", "nfl_nextGenStats_weekly.RData"))
```
